%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Vinamra}{Bhatia}{ } \\
\href{mailto:vinamrabhatia8@gmail.com}{vinamrabhatia8@gmail.com} | 8308814380 | f2015090@goa.bits-pilani.ac.in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection {\href{http://www.bits-pilani.ac.in/}{\custombold{BITS PILANI}} } 
\descript{BE(Hons) Computer Science}
\location{Expected Aug 2019 \\ CGPA: 8.41}
\sectionsep

\subsection{PMS Public School}
\location{Class XII, May 2015|  Moradabad, India}
\descript{CBSE - 96.8\%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/vinamrabhatia}{\custombold{vinamrabhatia}} \\
LinkedIn://  \href{https://www.linkedin.com/in/vinamrabhatia/}{\custombold{vinamrabhatia/}} \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{UnderGraduate}
Computer Architecture (In-progress) \\
Machine Learning (In-progress) \\
Operating Systems (In-progress) \\
Theory of Computation (In-progress) \\
Machine Learning (In-progress) \\
Network Programming (In-progress) \\
Data Structures and Algorithms \\
Microprocessors and Interfacing \\
Digital Design \\
Logic in Computer Science \\
Discrete Structures \\
Object Oriented Programming \\
Database Management Systems \\
Computer Programming \\
\sectionsep

\subsection{MOOCS}
Android Development \\
Usable Security \\
Cryptography \\
Development of Real Time Systems \\
Intro to Information Security \\
MetaSpoilt Unleashed \\
\sectionsep

\subsection{WORKSHOPS}
\href{http://www.bits-pilani.ac.in/}{\custombold{NetTech}} (stood 3rd among 150+) \\
Robocon Workshop \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
C \textbullet{}   C++ \textbullet{} Python \textbullet{} Lua \\
Java \textbullet{} JavaScript \textbullet{} SQL \textbullet{} Android \\ 
\section{Interests}
Penetration Testing \textbullet{} CyberSecurity \textbullet{} Computer Networks \textbullet{} Software Development
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection {\href{https://summerofcode.withgoogle.com/organizations/5824514215641088/6087291645722624/}{Google Summer of Code 2017}}
\descript{| {NMAP Network Scanner (Exploitation and Vulnerability Specialist) mentored by \href{http://calderonpale.com/}{\custombold{Paulino Calderon}}}}
\location{May 2017 - August 2017}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed and contributed to vulnerability scripts for NSE (NMAP Scripting Engine) which includes JSONP endpoint detection, SMBLoris detection, TR069 vulnerability, WordPress Content Injection Vulnerabilities
\item Worked on implementing a dedicated cookies library.
\item Added detection of several web-services, fixed some bugs in nmap repository.
\end{tightemize}
\sectionsep

\runsubsection {\href{http://hyperloopindia.in/}{SpaceX Hyperloop Pod Competition}}
\descript{| Software Engineer }
\location{Oct 2016 – Sept 2017 }
\begin{tightemize}
\item Worked on freeRTOS to develop software for a Prototype Hyperloop Pod and took the pod to SpaceX, Hawthrone, California during SpaceX Competition Weekend 2 (Aug 20 - Aug 26 '17) as part of Hyperloop India.
\item The team was among the top 24 teams from the world and the only team from India to have qualified for the same.
\end{tightemize}
\sectionsep

\runsubsection{i-Loads}
\descript{| Summer Intern }
\location{May 2017 – July 2017 }
\begin{tightemize}
\item Worked on making a Python Input-Output Master GUI.
\end{tightemize}
\sectionsep

\section{Projects}
\vspace{1mm}
\begin{tightemize}

\item Identification of Devanagari Manuscript : Optical Character Recognization of Devanagari Manuscript using OpenCV, numpy, matplotlib and scikit-learn. Sept 2017 - Present under Prof Ashwin Shrinivasan, BITS Goa

\item Synergy : Building a plugin based notification synchronization system for Android
and Linux devices. Sept 2017 - Present under Prof Mahadev Gawas.

\item \href{https://github.com/AutolabJS/AutolabJS}{Autolab Project} : An auto-grader system for evaluating labs. Worked on proper implementations of CA, Keys and Certificate and improved TLS implementation for the Autolab Project. (Jan 2017 - May 2017) under Prof Prasad Talasila, BITS Goa.

\item \href{https://ctftime.org/event/417}{BITSCTF} : Organized an international CTF(Capture the Flag) with the team(BITSkrieg). The hacking competition got great reviews and witnessed participation from over 500 international teams. (Jan 2017 - Feb 2017)

\item \href{https://play.google.com/store/apps/details?id=bits.mobileappclub.waves2016&hl=en}{Waves 2016 Mobile App} : Part of the team to build the Official Android App for one of the biggest cultural fest in the country. (Sept 2016 - Nov 2016)

\item Voizzle : Contributed in a voice based word puzzle game which used Google Speech API to detect words and highlight them in CrossWord. (Jan 2016 - Feb 2016)
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2017 		 & Google Summer of Code (around 1.2k students globally) \\
2016 		 & Google CTF 168th rank(global)\\
2015 		 & JEE Mains Rank 3015 among 15 lakh candidates\\
2013  		 & CBSE Proficiency Test 99.7 percentile\\
2011	     & \href{https://en.wikipedia.org/wiki/National_Talent_Search_Examination}{NTSE (National Talent Search Examination) Scholar}\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Position of Responsibilty}

\begin{tabular}{rll}
2017-18  & Coordinator, BITSkrieg (Official Club for Ethical Hacking and Penetration Testing)\\
2016-17  & Core Member, Mobile App Club, BITS Goa\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}